ARGoS-Blockchain interface

### 2020-09-12 article.tex
corrected folder

\title{ARGoS-Blockchain interface}
%\author{Volker Strobel \and Alex Pacheco \and Marco Dorigo}

@@

Several recent works have addressed the combination of blockchain
technology and swarm robotics
\cite{StrCasDor2018:aamas,StrDor2018:ants,StrFerDor2017:techreport-013,Cas2016:arxiv,PacStrDor2020:techreport-001,PacStrDor2020:techreport-007}. This
combination proves useful for security, consensus finding, robot
economies, robot-as-a-service, and potentially many other applications
in robot swarms. Being a young research field, it misses standardized
research platforms. However, conducting experiments involving robot
swarms and blockchain technology requires a suitable testbed. A widely
used framework consists of the Pi-puck robot platform running the
Ethereum blockchain network. However, not every researcher has access
to physical robots, obtaining and maintaining them be both
time-intense and cost-intense, not to mention the lengthy execution of
experiments. Therefore, a simulation testbed is needed to quickly try
and test different controllers and scenarios. The ARGoS robot swarm
simulator \citep{PinTriOGr-etal2012:si} is the state-of-the-art
research platform to conduct simulations in swarm robotics. Such a
framework proves useful both for researchers who do not have access to
a suitable robot platform, such as the Pi-puck robot. Additionally, a
suitable platform is important before running time- and cost-consuming
experiments with real robots.

@@

\begin{verbatim}
$ cd ARGoS-Blockchain-interface/ && cd geth/
$ git clone https://github.com/ethereum/go-ethereum.git custom-geth/
\end{verbatim}
% New item
\item Create the Ethereum image and initialize the Docker swarm.

>>>>

\title{ARGoS-Blockchain interface}
%\author{Volker Strobel \and Eduardo Castello Ferrer \ and Alex Pacheco \and Marco Dorigo}

@@

Several recent works have addressed the combination of blockchain
technology and swarm robotics
\cite{StrCasDor2018:aamas,StrDor2018:ants,StrFerDor2017:techreport-013,Cas2016:arxiv,PacStrDor2020:techreport-001,PacStrDor2020:techreport-007}. This
combination proves useful for security, consensus finding, robot
economies, robot-as-a-service, and potentially many other applications
in robot swarms. Being a young research field, it misses standardized
research platforms. However, conducting experiments involving robot
swarms and blockchain technology requires a suitable testbed. A widely
used framework consists of the Pi-puck robot platform running the
Ethereum blockchain network. However, not every researcher has access
to physical robots, obtaining and maintaining them be both
time-intense and cost-intense, not to mention the lengthy execution of
experiments. Therefore, a simulation testbed is needed to quickly try
and test different controllers and scenarios. The ARGoS robot swarm
simulator \citep{PinTriOGr-etal2012:si} is the state-of-the-art
research platform to conduct simulations in swarm robotics. Such a
framework proves useful both for researchers who do not have access to
a suitable robot platform, such as the Pi-puck robot. Additionally, a
suitable platform is important before running time-consuming
experiments with real robots.

@@

\begin{verbatim}
$ cd Blockchain-module/ && cd geth/
$ git clone https://github.com/ethereum/go-ethereum.git custom-geth/
\end{verbatim}
% New item
\item Create the Ethereum image and initialize the Docker swarm.
